---
title: "toto_LJ"
author: "Leah Jackson"
date: "10/20/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Offense vs. Indentities


#should do age as a histogram


# Bar for Offense Type and Demographic ID

# What is the gender, race, ethnicity, under18 breakdown for different crimes?

p <- offense type
q <- gender, race, age, ethnicity, under18

ggplot(dat, 
       aes(p, fill = q)) + 
  geom_bar() + 
  theme(legend.position = "right")

# Bar for State and Offense Type
p <- state
q <- offense type

ggplot(dat, 
       aes(p, fill = q)) + 
  geom_bar() + 
  theme(legend.position = "right")

# Bar for Offense Type, State, and Demographic ID

```{r}
p <- state
q <- offense type
t <- ethnicity

ggplot(dat$p, 
       aes(q, fill = t)) + 
  geom_bar() + 
  theme(legend.position = "right")
```


## Scatterplot for Age and Crime

p <- age
q <- offense type
t <- gender, race, ethnicity

ggplot(dat, aes(p, fill = q)) + geom_point(alpha = 0.3) +  geom_smooth(method = "loess")
```

## Date and Crime

p <- offense type 
d <- date

gplot(color = p) +
  geom_step(dat, 
            aes(x= d, y= ), 
            direction = "hv")


# Correlation with other demographic factors? (religion, political leaning etc.)

# Are crimes rates alleviated in areas with social support structures?

# Do crime rates increase in areas with other issues? (ex. Add socex data for food environmental (food desert) index, high poverty (median household income, high homelessness), population density (if we can get county crime data), average education level?