---
title: "toto_LJ"
author: "Leah Jackson"
date: "10/20/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import library}
library(ggplot2)
```


# Bar: Offense vs. Indentities
ui: add offense types
server: add offense type selection options

```{r}
ggplot(aggregate_edited, 
       aes(race, offense_type) + 
geom_bar() + 
theme(legend.position = "top"))
```


# Histogram: Age of offenses by state
ui: add offense types, select state
server: add offense type selection options, select state

```{r}
ggplot(aggregate_edited, aes(x= age)) + 
geom_histogram(color = "darkblue", 
               fill= "lightblue") + 
geom_vline(xintercept = mean(aggregate_edited$age), 
           linetype = "dashed", 
           size = 2, 
           color = "black")
```

# Bar for State and Offense Type

```{r}
ggplot(aggregate_edited, 
       aes(state_name, offense_type) + 
geom_bar() + 
theme(legend.position = "top"))
```

# Time & Crime


# Correlation with other demographic factors? (religion, political leaning etc.)



# Are crimes rates alleviated in areas with social support structures?

# Do crime rates increase in areas with other issues? (ex. Add socex data for food environmental (food desert) index, high poverty (median household income, high homelessness), population density (if we can get county crime data), average education level?